Comparing distance distributions for top predictive features between bins with and without TADs

### 2019-05-29 Scripts/comparing_distance_profiles_using_boxplots.Rmd
edits to results script

all_dist_gm12878$Resolution <- factor(all_dist_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

@@

# 10 kb
all_dist_gm12878_10kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("Transcription Factor\nBinding Site") +
  ylab("Log2 Distance") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 25 kb
all_dist_gm12878_25kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 50 kb
all_dist_gm12878_50kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 100 kb
all_dist_gm12878_100kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

figure <- ggarrange(all_dist_gm12878_25kb,
                    all_dist_gm12878_50kb,
                    all_dist_gm12878_100kb,
                    ncol = 1,
                    nrow = 3,
                    common.legend = TRUE,
                    legend = "top",
                    labels = "AUTO",
                    font.label = list(size=20))
figure 
annotate_figure(figure, 
                bottom = text_grob("Transcription Factor\nBinding Site", color = "black", size = 20),
                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
```

@@

all_dist_K562$Resolution <- factor(all_dist_K562$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

@@

# 10 kb
all_dist_K562_10kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 25 kb
all_dist_K562_25kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 50 kb
all_dist_K562_50kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

# 100 kb
all_dist_K562_100kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped\nw/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15#,
                                   #angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   #hjust = 1
                                   ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        strip.text.x = element_text(size = 15))

figure <- ggarrange(all_dist_K562_10kb,
                    all_dist_K562_25kb,
                    all_dist_K562_50kb,
                    all_dist_K562_100kb,
                    ncol = 2,
                    nrow = 2,
                    common.legend = TRUE,
                    legend = "top",
                    labels = "AUTO",
                    font.label = list(size=20))
figure 
annotate_figure(figure, 
                bottom = text_grob("Transcription Factor\nBinding Site", color = "black", size = 20),
                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
```

>>>>

all_dist_gm12878$y <- factor(all_dist_gm12878$y, levels=c("Yes","No"))
all_dist_gm12878$Resolution <- factor(all_dist_gm12878$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

@@

# 10 kb
all_dist_gm12878_10kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("Transcription Factor Binding Site") +
  ylab("Log2 Distance") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

# 25 kb
all_dist_gm12878_25kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

# 50 kb
all_dist_gm12878_50kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

# 100 kb
all_dist_gm12878_100kb <- ggplot(all_dist_gm12878[which(all_dist_gm12878$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("Transcription Factor Binding Site") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

figure <- ggarrange(all_dist_gm12878_25kb,
                    all_dist_gm12878_50kb,
                    all_dist_gm12878_100kb,
                    ncol = 1,
                    nrow = 3,
                    common.legend = TRUE,
                    legend = "bottom",
                    labels = "AUTO",
                    font.label = list(size=20))
figure 
annotate_figure(figure, 
                #bottom = text_grob("Transcription Factor Binding Site", color = "black", size = 20),
                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
```

@@

all_dist_K562$y <- factor(all_dist_K562$y, levels=c("Yes", "No"))
all_dist_K562$Resolution <- factor(all_dist_K562$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

@@

# 10 kb
all_dist_K562_10kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="10 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

# 25 kb
all_dist_K562_25kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="25 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

# 50 kb
all_dist_K562_50kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="50 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("Transcription Factor Binding Site") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

# 100 kb
all_dist_K562_100kb <- ggplot(all_dist_K562[which(all_dist_K562$Resolution=="100 kb"),], aes(x = y, y = value, fill = y)) +
  facet_grid(~ variable) +
  stat_boxplot(geom = "errorbar") +
  geom_boxplot() +
  stat_compare_means(comparisons = list(c("No", "Yes")), 
                     method = "wilcox.test", 
                     label = "p.signif") +
  #facet_grid(~ variable) +
  xlab("Transcription Factor Binding Site") +
  ylab("") +
  #ylim(5,25) +
  scale_fill_discrete(name="Genomic bin overlapped w/ flanked TAD boundary") +
  #guides(color=FALSE) +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        legend.position="bottom",
        strip.text.x = element_text(size = 15))

figure <- ggarrange(all_dist_K562_10kb,
                    all_dist_K562_25kb,
                    all_dist_K562_50kb,
                    all_dist_K562_100kb,
                    ncol = 2,
                    nrow = 2,
                    common.legend = TRUE,
                    legend = "bottom",
                    labels = "AUTO",
                    font.label = list(size=20))
figure 
annotate_figure(figure, 
                #bottom = text_grob("Transcription Factor Binding Site", color = "black", size = 20),
                left = text_grob("Log2 Distance", color = "black", size = 20, rot=90))
```
